Multi-Agent Pathfinding with Matching using Increasing Cost Tree Search

### 2021-06-27 docs/paper.tex
Fixed a few more typos

	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E. Bounded search outperforms unbounded search as expected, given that the former does as much work as the latter and often less. Approximate ordering outperforming unordered enumeration is not as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that ordered enumeration works well in practice. Simple pruning with child pruning outperforms exhaustive pruning but this needs to be qualified. Comparing Exh+S+B+O with Exh+E+B+O shows that part of the difference can be explained by the use of simple pruning instead of enhanced pruning. Nonetheless, in instances with 75\% wall (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}) there appears to be a real benefit to searching a smaller ICT. Across ICTS-m variants, similar trends can be observed but the differences across pruning strategies are too slight to draw any conclusions from. As discussed in Section \ref{future}, more work is needed to determine if such an improvement is to be expected more generally.

>>>>

	Between exhaustive variants, with exception of the ID variant, a type of hierarchy can be distinguished, best illustrated by \ref{fig:i-25-3-p}; almost without exception, Exh+S+C+B+O outperforms Exh+E+B+O which outperforms Exh+E+B which in turn outperforms Exh+E. Bounded search outperforms unbounded search as expected, given that the former does as much work as the latter and often less. Approximate ordering outperforming unordered enumeration is not as obvious from a theoretical standpoint, as discussed in \ref{ordered-enum}, and simply indicates that ordered enumeration works well in practice. Simple pruning with child pruning outperforms enhanced pruning but this needs to be qualified. Comparing Exh+S+B+O with Exh+E+B+O shows that part of the difference can be explained by the use of simple pruning instead of enhanced pruning. Nonetheless, in instances with 75\% wall (\ref{fig:i-75-1-p},\ref{fig:i-75-3-p}) there appears to be a real benefit to searching a smaller ICT. Across ICTS-m variants, similar trends can be observed but the differences across pruning strategies are too slight to draw any conclusions from. As discussed in Section \ref{future}, more work is needed to compare simple child pruning with other pruning methods for ICTS.
